COG-ED Manuscript

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
changed fig1 caption

```{r figure1, echo=FALSE, message=FALSE, warning=FALSE}
include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
```
*Fig.1* Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.

@@

```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back."}

>>>>

```{r figure1, echo=FALSE, message=FALSE, warning=FALSE}
include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
```
*Fig.1* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.

@@

```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back."}
